---
title: "Abacavirinol"
author: "Samantha Lee"
date: "Fall 2018"
output:
  html_document: default
  word_document: default
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
abac <-read.csv(file="abacavirinol.csv",header=TRUE)
View(abac)
```

```{r}
LBGTguys <- filter(abac, LBGT=="yes")
```

```{r}
males <- filter(abac, sex=="M")
females <- filter(abac, sex=="F")
```

```{r}
IVuser <- filter(abac, Ivdrug=="user")
```




# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides (abacavirinol) is under test in clinical trials. Analyze the effectiveness of this drug across the board. Consider population subgroups by gender, drug use, and sexual orientation. Finish this!

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

To decide the effectiveness of abacavirinol, we will determine the effectiveness of abacavirinol with all people, with men, with women, with individuals who identify as LBGT, and with drug users.


# Chapter 1 Overlall effectiveness of abacavirinol.

For this chapter, will will look at the overall effectiveness of abacavirinol with all groups invloved in the test.

## Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->


We will now look at a barchart to determine the overall effectiveness of abacavirinol. Since the collumn that contains people who recieved abacavirinol and contracted aids is smaller than the collumn that contains people who recieved abacavirinol and contracted aids, abacavirinol appears to be working.



```{r}
barchartGC(~infected + treatment, data=abac, type = "percent")
```





### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

Now we will look at a table of the percentage of those who received abacavirinol and contracted aids compared to the percentage of those who recieved the placebo and contracted aids.  Looking at the collumn percentages, people who recieved abacavirinol only made up 40.93 percent of the people who got aids which is 18.14 percent less than the people who got aids and who recieved the placebo (59.07 percent).


```{r}
tab1 =xtabs(~treatment+infected, data=abac)
rowPerc(tab1)
colPerc(tab1)
```


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

$H_0$ The number of people who take abacavirinol and recieved aids ≥ 50%.

$H_a$ The number of people who take abacavirinol and recieved < 50%.


We will now run a Chi-squared test and a Fisher's exact test to determine the significance of this data.  The P-value is .0168; since it is lower than .05 we reject the null hypothesis and accept the alternative.

```{r}
chisq.test(tab1)
chisqtestGC(tab1)
fisher.test(tab1)
```


## Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->


According to our graphical and nummerical results, less people who took abacavirinol contracted the aids virus than those who recieved the placebo. Since the P-value is .0168, which is less than .05, we reject the null hypothesis and accept the alternative. The significance of the results leads us to believe that, for everyone in the study together, abacavirinol does help to prevent the contraction of aids.


# Chapter 2 Abacavirinol effectiveness with LBGT individuals

For this chapter, will now look at the effectiveness of abacavirinol with individuals who identify as LBGT.


## Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

We will now create a barchart to compare the amount of people who contracted the aids virus after recieving abacavirinol to those who recieved the placebo. Looking at the results, more people contracted the aids virus who recieved the drug than those who recieved the placebo.  Abacavirinol appears to be having the opposite effect than intended.

```{r}
barchartGC(~infected + treatment, data=LBGTguys, type = "percent")
```





### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

We will now create a table of the perecentage of those who recieved abacavirinol and contracted aids to those who recieved the placebo and contracted aids.  Looking at the collumn percent, 68.97 percent of those who contracted aids had recieved abacavirinol while the people who recieved the placebo only made up 31.03 percent of those infected.


```{r}
tab2 =xtabs(~treatment+infected, data=LBGTguys)
rowPerc(tab2)
colPerc(tab2)
```


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


$H_0$ The number of LBGT people who take abacavirinol and recieved aids ≥ 50%.

$H_a$ The number of LBGT people who take abacavirinol and recieved < 50%.

We will now run a Chi-squared test and a Fisher's exact test to determine the significance of these results.  The P-value is .0743.  The P-value is more than .05 so we fail to reject the null hypothesis.

```{r}
chisq.test(tab2)
chisqtestGC(tab2)
fisher.test(tab2)
```



## Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

Looking at our graphical and numerical test results, abacavirinol had the opposite effect than intended with more LBGT individuals contracting the aids virus than those who recieved the placebo.  Since the P-value is .0743, which is greater than .05, we fail to reject the null hypothesis. This supports abacavirinol not working with LBGT individuals.


# Chapter 3 Abacavirinol effectiveness with men

For this chapter, we will look at the effectiveness of abacavirinol with men.

##Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

We will now create a bargraph to compare the amount of men who contracted aids after recieving abacavirinol compared to those who recieved the placebo.  Looking at the chart, men who recieved abacavirinol contracted aids less than those who received the placebo. Abacavirinol appears to be working for men.

```{r}
barchartGC(~infected + treatment, data=males, type = "percent")
```





### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

We will now create a table to compare the number of men who took abacavirinol and contracted aids to the number of men who recieved the placebo and contracted aids. Looking at the column precents, men who received the abacavirinol made up 30.46 percent of the men who contracted aids while men who recieved the placebo made up 69.54 percent.  


```{r}
tab3 =xtabs(~treatment+infected, data=males)
rowPerc(tab3)
colPerc(tab3)
```


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


$H_0$ The number of men who take abacavirinol and recieved aids ≥ 50%.

$H_a$ The number of men who take abacavirinol and recieved < 50%. 

We will now run a Chi-squared test and a Fisher's exact test to determine the significance of these results. The P-value is 6.052e-06; since it is less than .05, we reject the null and accept the alternative.


```{r}
chisq.test(tab3)
chisqtestGC(tab3)
fisher.test(tab3)
```


## Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->


Looking at the graphical and numerical results, abacavirinol works for the men since less men who recieved abacavirinol contracted aids than those who received the placebo.  Since the P-value is 6.052-e06 which is less than .05, we rejected the null hypothesis and accepted the null, supporting abacavirinol working for men.


# Chapter 4 Effectiveness with women

For this chapter, we will look at the effectiveness of abacavirinol with women.

##Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

We will now create a barchat to compare the amount of women who received abacavirinol and contracted aids with the amount of women who recieved the placebo and contracted aids. Looking at the chart, women who received abacavirinol contracted aids than those who received the placebo. Abacavirinol seems to be having the opposite effect than intended.


```{r}
barchartGC(~infected + treatment, data=females, type = "percent")
```





### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

We will now create a table to compare the amount of women who recieved abacavirinol and contracted aids to those who recieved the placebo and contracted aids.  Looking at the collumn percent of women who contracted aids, 59.3 percent of the women who recieved abacavirinol contracted aids while 40.7 percent of the women who recieved the placebo contracted aids. 18.6 percent more women who recieved abacavirinol contracted aids than women who recieved the placebo.


```{r}
tab4 =xtabs(~treatment+infected, data=females)
rowPerc(tab4)
colPerc(tab4)
```


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


$H_0$ The number of women who take abacavirinol and recieved aids ≥ 50%. 

$H_a$ The number of women who take abacavirinol and recieved aids < 50%.

We will now run a Chi-squared test and a Fisher's exact test to determine the significance of these results.  The P-value is .06195. Since it is greater than .05, we fail to rejec the null hypothesis. This supports that the drug does not work with women.

```{r}
chisq.test(tab4)
chisqtestGC(tab4)
fisher.test(tab4)
```


## Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

Looking at the graphical and numerical results, the drug is having the opposite of the intended effect on women.  The inferential results determined we fail to reject the null, supporting that this drug is not effective for women.

# Chapter 5 Effectiveness with drug users

For this chapter, will observe the effectiveness of abacavirinol with drug users.


##Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

We will now create a barchart to compare the number of drug users who recieved abacavirinol and contracted aids with drug users who recieved the placebo and contracted aids. Looking at the chart, less drug users who recieved abacavirinol contracted aids than that recieved the placebo. Abacavirinol appears to be working.

```{r}
barchartGC(~infected + treatment, data=IVuser, type = "percent")
```



### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

We will now create a table to compare the amount of drug users who recieved abacavirinol and contracted aids to the amount of drug users who recieved the placebo and contracted aids.  25.64 percent of those who contracted aids received abacavirinol 74.36 percent of those who contracted aids recieved the placebo. Drug users who recieved abacavirinol made up 48.72 less of the people who contracted aids than drug users who recieved the placebo.

```{r}
tab5 =xtabs(~treatment+infected, data=IVuser)
rowPerc(tab5)
colPerc(tab5)
```


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


$H_0$ The number of drug users who take abacavirinol and recieved aids ≥ 50%.

$H_a$ The number of drug users who take abacavirinol and recieved < 50%.


We will now run a Chi-squared test and a Fisher's exact test to determine the statistical significance of these results.  The P-value is .02266 which is less than .05.  This means we will reject the null hypothesis and accept the altenative.  These results support the drug working.



```{r}
chisq.test(tab5)
chisqtestGC(tab5)
fisher.test(tab5)
```


## Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

Looking at the graphical and numerical results, abacavirinol is working since less drug users who recieved abacavirinol contracted aids than that recieved the placebo.  The inferential results supports this since the P-value is .02266, less than .05.
